Tempo Analysis: The Sound of Teaching Music 2

### 2020-12-03 analysis/stats/ioi.Rmd

---
title: 'Tempo Analysis: The Sound of Teaching Music 1'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

# IOI-Articulation 
## 1. All - individual{#art_ind_all}
- Average IOIs for each participant.

```{r ioi-art, echo = FALSE}
# For each individual
ioi_art <- dt_ioi_art[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill)]
ioi_art
```

### Plot
#### Boxplot
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).

```{r ioi-art-box,  echo = FALSE}
ggboxplot(dt_ioi_art[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr)], "SubNr", "Mean", color = "Condition", palette = "aaas", xlab = "SubNr", ylab = "IOIs (ms)", title = "IOI: Articulation") + 
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  geom_hline(yintercept = 188, linetype = "dashed")
```

## 2. All - group{#art_group_all}
- Average IOIs for each condition.
- Hypothesis: Participants will play slower when teaching.

@@

### Plot
#### Box plot
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).

@@

ggpaired(ioi_art_plot, cond1 = "performing", cond2 = "teaching", color = "condition", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Articulation") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica Neue LT Std 57 Condensed")
```

### Statistics
#### Normality check
- Violate the normality for differences between the two conditions

@@

@@

## 3. Phrase boundaries - individual{#art_ind_phrase}
- Compare IOIs at phrase boundaries with others for each participant.

@@

# For each individual
ioi_art_ch <- dt_ioi_art[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, Boundary)]
ioi_art_ch
```

### Plot
#### Box plot
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).

```{r ioi-art-ch-box, echo = FALSE}
ggboxplot(dt_ioi_art[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr, Boundary)], "SubNr", "Mean", color = "Condition", palette = "aaas", xlab = "SubNr", ylab = "IOIs (ms)", title = "IOI: Articulation") + 
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  facet_grid(Boundary ~ .) +
  geom_hline(yintercept = 188, linetype = "dashed")
```

## 4. Phrase boundaries - group{#art_group_phrase}
- Compare IOIs at phrase boundaries with others in the two conditions.
- Hypothesis: Participants will play more slowly at phrase boundaries compared to other locations (especially for teaching purposes).

@@

### Plot
#### Box plot
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).

@@

ggpaired(ioi_art_ch_plot, cond1 = "performing", cond2 = "teaching", color = "condition", facet.by = "boundary", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Articulation") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica Neue LT Std 57 Condensed")
```

@@

## 5. Trial by trial - individual{#art_ind_trial}
- Average IOIs for each trial for each participant.

```{r ioi-art-trial, echo = FALSE}
# For each individual
ioi_art_trial <- dt_ioi_art[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, TrialNr)]
ioi_art_trial
```

### Plot
#### Line graph
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).

```{r ioi-art-trial-line, echo = FALSE, fig.height = 4}
ggline(dt_ioi_art[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr)], x = "TrialNr", y = "Mean", shape = "Condition", color = "Condition", palette = "aaas", xlab = "TrialNr", ylab = "IOIs (ms)", title = "IOI: Articulation") +
  facet_wrap(SubNr ~ .) +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,8,1)) +
  geom_hline(yintercept = 188, linetype = "dashed")
```

## 6. Trial by trial - group{#art_group_trial}
- Average IOIs for each trial for each condition.

@@

### Plot
#### Line graph
- Error bars show SEM of the mean
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).

```{r ioi-art-trial-all-line, echo = FALSE}
ggline(ioi_art_trial, x = "TrialNr", y = "Mean", add = "mean_se", position = position_dodge(.2), shape = "Condition", color = "Condition", palette = "aaas", xlab = "Trial", ylab = "IOIs (ms)", title = "IOI: Articulation") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,8,1))
```

# IOI-Dynamics
## 1. All - individual{#dyn_ind_all}
- Average IOIs for each participant.

```{r ioi-dyn, echo = FALSE}
# For each individual
ioi_dyn <- dt_ioi_dyn[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill)]
ioi_dyn
```

### Plot
#### Box plot
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).

```{r ioi-dyn-box,  echo = FALSE}
ggboxplot(dt_ioi_dyn[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr)], "SubNr", "Mean", color = "Condition", palette = "aaas", xlab = "SubNr", ylab = "IOIs (ms)", title = "IOI: Dynamics") + 
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  geom_hline(yintercept = 188, linetype = "dashed")
```

## 2. All - group{#dyn_group_all}
- Average IOIs for each condition.
- Hypothesis: Participants will play slower when teaching.

@@

ggpaired(ioi_dyn_plot, cond1 = "performing", cond2 = "teaching", color = "condition", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Dynamics") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica Neue LT Std 57 Condensed")
```

### Statistics
#### Normality check
- Violate the normality for differences between the two conditions

@@

@@

## 3. Phrase boundaries - individual{#dyn_ind_phrase}
- Compare IOIs at phrase boundaries with others for each participant.

@@

# For each individual
ioi_dyn_ch <- dt_ioi_dyn[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, Boundary)]
ioi_dyn_ch
```

### Plot
#### Box plot
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).

```{r ioi-dyn-ch-box, echo = FALSE}
ggboxplot(dt_ioi_dyn[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr, Boundary)], "SubNr", "Mean", color = "Condition", palette = "aaas", xlab = "SubNr", ylab = "IOIs (ms)", title = "IOI: Dynamics") + 
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  facet_grid(Boundary ~ .) +
  geom_hline(yintercept = 188, linetype = "dashed")
```

## 4. Phrase boundaries - group{#dyn_group_phrase}
- Compare IOIs at phrase boundaries with others in the two conditions.
- Hypothesis: Participants will play more slowly at phrase boundaries compared to other locations (especially for teaching purposes).

@@

ggpaired(ioi_dyn_ch_plot, cond1 = "performing", cond2 = "teaching", color = "condition", facet.by = "boundary", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Dynamics") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica Neue LT Std 57 Condensed")
```

@@

## 5. Trial by trial - individual{#dyn_ind_trial}
- Average IOIs for each trial for each participant.

```{r ioi-dyn-trial, echo = FALSE}
# For each individual
ioi_dyn_trial <- dt_ioi_dyn[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, TrialNr)]
ioi_dyn_trial
```

### Plot
#### Line graph
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).

```{r ioi-dyn-trial-line, echo = FALSE, fig.height = 4}
ggline(dt_ioi_dyn[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr)], x = "TrialNr", y = "Mean", shape = "Condition", color = "Condition", palette = "aaas", xlab = "TrialNr", ylab = "IOIs (ms)", title = "IOI: Dynamics") +
  facet_wrap(SubNr ~ .) +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,8,1)) +
  geom_hline(yintercept = 188, linetype = "dashed")
```

## 6. Trial by trial - group{#dyn_group_trial}
- Average IOIs for each trial for each condition.

@@

### Plot
#### Line graph
- Error bars show SEM of the mean
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms).

```{r ioi-dyn-trial-all-line, echo = FALSE}
ggline(ioi_dyn_trial, x = "TrialNr", y = "Mean", add = "mean_se", position = position_dodge(.2), shape = "Condition", color = "Condition", palette = "aaas", xlab = "Trial", ylab = "IOIs (ms)", title = "IOI: Dynamics") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,8,1))
```
# Sequence plot
## Articulation{#sequence_art}
```{r seq-art, fig.width = 9, fig.height = 3, echo = FALSE}
# For each individual
ioi_art_seq <- dt_ioi_art[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, Interval)]

ggline(ioi_art_seq, x = "Interval", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Interval", ylab = "IOIs (ms)", title = "IOI: Articulation") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,66,1))
```

## Dynamics{#sequence_dyn}
```{r seq-dyn, fig.width = 9, fig.height = 3, echo = FALSE}
# For each individual
ioi_dyn_seq <- dt_ioi_dyn[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, Condition, Skill, Interval)]

ggline(ioi_dyn_seq, x = "Interval", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Interval", ylab = "IOIs (ms)", title = "IOI: Dynamics") +
  geom_hline(yintercept = 188, linetype = "dashed") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
    scale_x_continuous(breaks = seq(1,66,1))
```

>>>>

---
title: 'Tempo Analysis: The Sound of Teaching Music 2'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

# IOI-Articulation 
## 1. All - individual{#art_ind_all}
- Average normIOIs for each participant.

```{r ioi-art, echo = FALSE}
# For each individual
ioi_art <- dt_ioi_art[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill)]
ioi_art
```

### Plot
#### Boxplot
- A dashed line represents the tempo given by a metronome.

```{r ioi-art-box,  echo = FALSE}
ggboxplot(dt_ioi_art[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr)], "SubNr", "Mean", color = "Condition", palette = "aaas", xlab = "SubNr", ylab = "Normalised IOIs", title = "IOI: Articulation") + 
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  geom_hline(yintercept = 1, linetype = "dashed")
```

## 2. All - group{#art_group_all}
- Average normIOIs for each condition.
- Hypothesis: Participants will play slower when teaching.

@@

### Plot
#### Box plot
- A dashed line represents the tempo given by a metronome.

@@

ggpaired(ioi_art_plot, cond1 = "performing", cond2 = "teaching", color = "condition", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "Normalised IOIs", title = "IOI: Articulation") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica Neue LT Std 57 Condensed")
```

### Statistics
#### Normality check

@@

#### Paired *t*-test

```{r paired-art, echo = FALSE}
ioi_art_ttest <- t.test(ioi_art[Condition == "teaching"]$Mean, ioi_art[Condition == "performing"]$Mean, paired = TRUE, alternative = "two.sided")
ioi_art_ttest
```

@@

## 3. Phrase boundaries - individual{#art_ind_phrase}
- Compare normIOIs at phrase boundaries with others for each participant.

@@

# For each individual
ioi_art_ch <- dt_ioi_art[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, Boundary)]
ioi_art_ch
```

### Plot
#### Box plot
- A dashed line represents the tempo given by a metronome.

```{r ioi-art-ch-box, echo = FALSE}
ggboxplot(dt_ioi_art[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr, Boundary)], "SubNr", "Mean", color = "Condition", palette = "aaas", xlab = "SubNr", ylab = "Normalised IOIs", title = "IOI: Articulation") + 
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  facet_grid(Boundary ~ .) +
  geom_hline(yintercept = 1, linetype = "dashed")
```

## 4. Phrase boundaries - group{#art_group_phrase}
- Compare normIOIs at phrase boundaries with others in the two conditions.
- Hypothesis: Participants will play more slowly at phrase boundaries compared to other locations (especially for teaching purposes).

@@

### Plot
#### Box plot
- A dashed line represents the tempo given by a metronome (80bpm / IOI-188ms)

@@

ggpaired(ioi_art_ch_plot, cond1 = "performing", cond2 = "teaching", color = "condition", facet.by = "boundary", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "Normalised IOIs", title = "IOI: Articulation") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica Neue LT Std 57 Condensed")
```

@@

## 5. Trial by trial - individual{#art_ind_trial}
- Average normIOIs for each trial for each participant.

```{r ioi-art-trial, echo = FALSE}
# For each individual
ioi_art_trial <- dt_ioi_art[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, TrialNr)]
ioi_art_trial
```

### Plot
#### Line graph
- A dashed line represents the tempo given by a metronome.

```{r ioi-art-trial-line, echo = FALSE, fig.height = 4}
ggline(dt_ioi_art[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr)], x = "TrialNr", y = "Mean", shape = "Condition", color = "Condition", palette = "aaas", xlab = "TrialNr", ylab = "Normalised IOIs", title = "IOI: Articulation") +
  facet_wrap(SubNr ~ .) +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,8,1)) +
  geom_hline(yintercept = 1, linetype = "dashed")
```

## 6. Trial by trial - group{#art_group_trial}
- Average normIOIs for each trial for each condition.

@@

### Plot
#### Line graph
- Error bars show SEM of the mean
- A dashed line represents the tempo given by a metronome.

```{r ioi-art-trial-all-line, echo = FALSE}
ggline(ioi_art_trial, x = "TrialNr", y = "Mean", add = "mean_se", position = position_dodge(.2), shape = "Condition", color = "Condition", palette = "aaas", xlab = "Trial", ylab = "Normalised IOIs", title = "IOI: Articulation") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,8,1))
```

# IOI-Dynamics
## 1. All - individual{#dyn_ind_all}
- Average normIOIs for each participant.

```{r ioi-dyn, echo = FALSE}
# For each individual
ioi_dyn <- dt_ioi_dyn[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill)]
ioi_dyn
```

### Plot
#### Box plot
- A dashed line represents the tempo given by a metronome.

```{r ioi-dyn-box,  echo = FALSE}
ggboxplot(dt_ioi_dyn[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr)], "SubNr", "Mean", color = "Condition", palette = "aaas", xlab = "SubNr", ylab = "Normalised IOIs", title = "IOI: Dynamics") + 
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  geom_hline(yintercept = 1, linetype = "dashed")
```

## 2. All - group{#dyn_group_all}
- Average normIOIs for each condition.
- Hypothesis: Participants will play slower when teaching.

@@

ggpaired(ioi_dyn_plot, cond1 = "performing", cond2 = "teaching", color = "condition", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "Normalised IOIs", title = "IOI: Dynamics") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica Neue LT Std 57 Condensed")
```

### Statistics
#### Normality check

@@

#### Paired *t*-test

```{r paired-dyn, echo = FALSE}
ioi_dyn_ttest <- t.test(ioi_dyn[Condition == "teaching"]$Mean, ioi_dyn[Condition == "performing"]$Mean, paired = TRUE, alternative = "two.sided")
ioi_dyn_ttest
```

@@

## 3. Phrase boundaries - individual{#dyn_ind_phrase}
- Compare normIOIs at phrase boundaries with others for each participant.

@@

# For each individual
ioi_dyn_ch <- dt_ioi_dyn[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, Boundary)]
ioi_dyn_ch
```

### Plot
#### Box plot
- A dashed line represents the tempo given by a metronome.

```{r ioi-dyn-ch-box, echo = FALSE}
ggboxplot(dt_ioi_dyn[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr, Boundary)], "SubNr", "Mean", color = "Condition", palette = "aaas", xlab = "SubNr", ylab = "Normalised IOIs", title = "IOI: Dynamics") + 
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  facet_grid(Boundary ~ .) +
  geom_hline(yintercept = 1, linetype = "dashed")
```

## 4. Phrase boundaries - group{#dyn_group_phrase}
- Compare normIOIs at phrase boundaries with others in the two conditions.
- Hypothesis: Participants will play more slowly at phrase boundaries compared to other locations (especially for teaching purposes).

@@

ggpaired(ioi_dyn_ch_plot, cond1 = "performing", cond2 = "teaching", color = "condition", facet.by = "boundary", line.size = 0.3, line.color = "gray", palette = "aaas", xlab = "Condition", ylab = "Normalised IOIs", title = "IOI: Dynamics") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "none", base_family = "Helvetica Neue LT Std 57 Condensed")
```

@@

## 5. Trial by trial - individual{#dyn_ind_trial}
- Average normIOIs for each trial for each participant.

```{r ioi-dyn-trial, echo = FALSE}
# For each individual
ioi_dyn_trial <- dt_ioi_dyn[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, TrialNr)]
ioi_dyn_trial
```

### Plot
#### Line graph
- A dashed line represents the tempo given by a metronome.

```{r ioi-dyn-trial-line, echo = FALSE, fig.height = 4}
ggline(dt_ioi_dyn[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr)], x = "TrialNr", y = "Mean", shape = "Condition", color = "Condition", palette = "aaas", xlab = "TrialNr", ylab = "Normalised IOIs", title = "IOI: Dynamics") +
  facet_wrap(SubNr ~ .) +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,8,1)) +
  geom_hline(yintercept = 1, linetype = "dashed")
```

## 6. Trial by trial - group{#dyn_group_trial}
- Average normIOIs for each trial for each condition.

@@

### Plot
#### Line graph
- Error bars show SEM of the mean
- A dashed line represents the tempo given by a metronome.

```{r ioi-dyn-trial-all-line, echo = FALSE}
ggline(ioi_dyn_trial, x = "TrialNr", y = "Mean", add = "mean_se", position = position_dodge(.2), shape = "Condition", color = "Condition", palette = "aaas", xlab = "Trial", ylab = "Normalised IOIs", title = "IOI: Dynamics") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  theme_pubr(base_size = 20, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,8,1))
```
# Sequence plot
## Articulation{#sequence_art}
```{r seq-art, fig.width = 9, fig.height = 3, echo = FALSE}
# For each individual
ioi_art_seq <- dt_ioi_art[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, Interval)]

ggline(ioi_art_seq, x = "Interval", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Interval", ylab = "Normalised IOIs", title = "IOI: Articulation") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
  scale_x_continuous(breaks = seq(1,71,1))
```

## Dynamics{#sequence_dyn}
```{r seq-dyn, fig.width = 9, fig.height = 3, echo = FALSE}
# For each individual
ioi_dyn_seq <- dt_ioi_dyn[, .(N = .N, Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, Condition, Skill, Interval)]

ggline(ioi_dyn_seq, x = "Interval", y = "Mean", add = "mean_se", position = position_dodge(.2), linetype = "Condition", shape = "Condition", color = "Condition", palette = "aaas", xlab = "Interval", ylab = "Normalised IOIs", title = "IOI: Dynamics") +
  geom_hline(yintercept = 1, linetype = "dashed") +
  theme_pubr(base_size = 12, legend = "bottom", base_family = "Helvetica Neue LT Std 57 Condensed") +
    scale_x_continuous(breaks = seq(1,71,1))
```
